---
title: "Visualize the Results"
author: "Yi Feng & Gregory R. Hancock"
#date: "`r Sys.Date()`"
output:
      rmarkdown::html_vignette:
        fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## <span style="color:seagreen">**Visualize the Results**</span> 


To visualize the missing data patterns of the optimal PHPM design, we can use the `plotPM()` function with the `simPM()` object. It will plot the missing data pattern matrix so people can have a more intuitive understanding of the optimal design that was selected. 

```{r, echo=FALSE,message=FALSE,warning=FALSE}
setwd("C:/Users/yifeng94/Desktop/simPM/simPM-git/examples")
load("wave.ex2_r1.rda")
load("item.ex2_r1.rda")
#load("forward.ex2_r1.rda")
library(simPM)
```


## <span style="color:seagreen">**Examples**</span> 

Below is an example of the plot showing the missing data patterns for a wave-level PHPM design. It corresponds to the missing data pattern matrix in the output summary. By default, the plot will use red (`"firebrick"`) to indicate missingness and beige (`"antiquewhite1"`) to indicate complete data. In the plot, each row represents a unique missing data pattern. Each column represents an observed variable. The number of participants assigned to each missing data pattern is labeled by the missing data pattern. 

```{r,fig.width=7,fig.height=4}

plotPM(wave.ex2, fontsize_col = 15)

```


We can change the color scheme of the plot by setting `col = `. 

```{r,fig.width=7,fig.height=4}
plotPM(wave.ex2, col = c("gray96", "gray35"), fontsize_col = 15)
```


We can also turn off the wave label by using the `labels = FALSE` argument.

```{r,fig.width=7,fig.height=4}
plotPM(wave.ex2, labels = F, col = c("gray96", "gray35"), fontsize_col = 15)
```


Below is an example of the plot showing the missing data patterns for a item-level PHPM design. If we do not wish to include the number of participants assigned to each missing data pattern, we can turn it off by setting `row.names = FALSE`.

```{r,fig.width=9,fig.height=6}
plotPM(item.ex2, row.names=F, fontsize_col = 15)
```




